X\texorpdfstring{\textsuperscript{2}}-Toon: An Extended X-Toon Shader

### 2013-04-11 paper/paper.tex
Adding images. They overlap (will fix)

\section{Tone Detail}
\label{sec:tonedetail}
\begin{wrapfigure}{r}{0.1\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.1\textwidth]{images/xtoon_skin}
  \end{center}
  \caption{2D Texture.}
  \vspace{-10pt}
  \label{fig:2dtexture}
\end{wrapfigure}
We extend the concept of a regular toon shader by adding a second dimension to the texture. While the x-axis remains as $N\cdot L$, where {\it{N}} is the surface normal and {\it{L}} is the light direction, the y-axis represents the level of detail. The higher up on the axis, the less detail is used. Conversely, the lower the y-axis value, the more detail. An example of a 2D texture used in this application can be seen in Figure~\ref{fig:2dtexture}.

@@

\subsection{Distance}
We developed a new method to determine the x-axis value based on the lighting of a scene. The direction to each light in the scene is determined for every vertex. These directions would then be summed and a resulting direction vector would be created. The direction vector is normalized and the final detail is calculated using the same equation for determining the

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=2.5in]{images/textures}
	\caption{A model without and with original textures applied, respectively}
	\label{fig:texturing}
\end{figure}

\subsection{Texture transparency}

\begin{figure}
	\centering
	\includegraphics[width=2.5in]{images/transparency}
	\caption{Transparency affecting output}
	\label{fig:transparency}
\end{figure}

\section{Results}
\label{sec:results}

\begin{figure}[ht]
  \centering
  \includegraphics[width=2.5in]{images/test}
  \caption{Sample illustration.}
\end{figure}

>>>>

\section{Tone Detail}
\label{sec:tonedetail}
\begin{wrapfigure}{r}{0.1\textwidth}
  \vspace{-20pt}
  \begin{center}
    \includegraphics[width=0.1\textwidth]{images/xtoon_skin}
  \end{center}
  \caption{2D Texture.}
  \vspace{-10pt}
  \label{fig:2dtexture}
\end{wrapfigure}
We extend the concept of a regular toon shader by adding a second dimension to the texture. While the x-axis remains as $N\cdot L$, where {\it{N}} is the surface normal and {\it{L}} is the light direction, the y-axis represents the level of detail. The higher up on the axis, the less detail is used. Conversely, the lower the y-axis value, the more detail. An example of a 2D texture used in this application can be seen in Figure~\ref{fig:2dtexture} (note the y-axis increases downward).

@@

\subsection{Distance}
As in the original X-Toon paper, one attribute map uses the focal distance of the vertex to the camera. The larger this distance, the less detail will be used, abstracting the model. The smaller this distance, the more detail used. Nothing was changed from the original paper. An example result can be seen in Figure~\ref{fig:distanceResult}, using a transparent texture map (see Section~\ref{sec:transparency}).

\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{images/distance_result}
	\caption{Parts of the model that are farther away are more transparent than closer areas.}
	\label{fig:distanceResult}
\end{figure}

@@

The negative of the look at vector is used because it is pointed towards the surface (see Figure~\ref{fig:angle}). This value indicates what surfaces the camera is directly pointed at. The amount of detail used decreases as the angle between the look at vector and the surface normal approaches $180^\circ$, or when the surface is completely pointed away from the camera (or vice versa). As the angle approaches 0, more detail is used. An example result of this attribute map can be seen in Figure~\ref{fig:angleResult}.

\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{images/angle_result}
	\caption{An example result of the angle attribute map/}
	\label{fig:angleResult}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/angle}
	\caption{Diagram of the angle calculation using the camera (left)'s look at vector and the surface normal (right). The angle difference is calculated (bottom right) using Equation~\ref{eqn:angle}.}
	\label{fig:angle}
\end{figure}

\subsection{Light Direction}
We developed a new method to determine the x-axis value based on the lighting of a scene. The direction to each light in the scene is determined for every vertex. These directions would then be summed and a resulting direction vector would be created. The direction vector is normalized and the final detail is calculated using the same equation for determining the

\begin{figure}[h]
	\centering
	\includegraphics[width=1.5in]{images/light_detail}
	\caption{A diagram explaining the light direction attribute map.}
	\label{fig:lightDirection}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=3.0in]{images/light_directions}
	\caption{An example result of using the light direction attribute map.}
	\label{fig:lightDirectionResult}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=3.0in]{images/textures}
	\caption{A model without and with original textures applied, respectively}
	\label{fig:texturing}
\end{figure}

\subsection{Texture transparency}
\label{sec:transparency}

\begin{figure}[h]
	\centering
	\includegraphics[width=2.5in]{images/transparency}
	\caption{Transparency affecting output}
	\label{fig:transparency}
\end{figure}

\section{Results}
\label{sec:results}
Some results are ablkjalskdjalskdjasd.

\begin{figure}[h]
	\centering
	\includegraphics[width=5.5in]{images/hologram}
	\caption{Hologram result}
	\label{fig:hologram}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=5.5in]{images/inverse_lighting}
	\caption{Inverse Lighting result}
	\label{fig:inverseLighting}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=5.5in]{images/lighting}
	\caption{Lighting result}
	\label{fig:lightingResult}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result1}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch1}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=5.5in]{images/stipple-hatch-result2}
	\caption{Stipple/hatching result}
	\label{fig:stippleHatch2}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=5.5in]{images/test}
  \caption{Sample illustration.}
\end{figure}
